Multiset-trie data structure

### 2022-08-01 tex/tex/s_intro.tex
Riste remarks (from the bus)
English checked and updated in s_data_structure and s_operations.

\medskip\noindent\textbf{Contributions.}\;
The main contributions of this paper are as follows. First, a  multiset-trie is a novel data structure for storing and querying a set of multisets that provides efficient multiset containment operations. Furthermore, the contributions of this work are thorough mathematical and empirical analyses of the proposed data structure multiset-trie.

Second, a mathematical model is developed to analyze the complexity of multiset containment operations. In particular, we estimate the size of a sub-tree traversed by a containment query and give an insight into the time complexity of containment queries. 
In addition to the mathematical analysis, the size of a sub-tree visited by a multiset containment query is also the central focus of the empirical analysis. We carefully designed the experiments to unravel the main features of the time complexity space. 
%%% relats btwn math and emprcl anlyss
%%% concrete results? bounds, ...
%%% experiments confirm findings of math analysis?

Finally, the mathematical as well as empirical analyses show an influence of ordering the elements of multisets on the efficiency of storing and processing multisets. We show that the ordering, which is based on the frequencies of the multiset elements, can speed up the multiset containment queries by orders of magnitude.

>>>>

\medskip\noindent\textbf{Contributions.}\;
The main contributions of this paper are as follows. First, a  multiset-trie is a novel data structure for storing and querying a set of multisets that provides efficient multiset containment operations.

Second, a mathematical model is developed to analyze the complexity of multiset containment operations. In particular, we estimate the size of a sub-tree traversed by a containment query and give an insight into the time complexity of containment queries. 
In addition to the mathematical analysis, the size of a sub-tree visited by a multiset containment query is also the central focus of the empirical analysis. We carefully designed the experiments to unravel the main features of the time complexity space.

Finally, the mathematical, as well as empirical analyses, show an influence of ordering the elements of multisets on the efficiency of storing and processing multisets. We show that the ordering, which is based on the frequencies of the multiset elements, can speed up the multiset containment queries by orders of magnitude.
